Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-22 latex/article.tex
minor edit

Representing a hierachical structure on GPU is usually challenging since the GPU
memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
to huge payload from cache misses.  Efficient spatial tree encoding can be
achieved using pointerless structures. We use linear quadtrees or octrees to
represent classical quadtree/octree trees, see for instance
\textsc{Gargantini}~\cite{gargantini1982effective}. This structure consists in
indexing each cell by a \emph{Morton code}: the code of children cells are
defined by the code of the parent suffixed by two bits (in dimension 2, three
bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
A cell's code encodes its position with respect to its parent cell and its
complete path to the tree root. Hence, whatever their depth, all cell codes are
simply stored in a linear vector on memory. Furthermore, cell operations such as
subdivision, merging, neighbors access can be efficiently implemented using
bitwise operations on the Morton code. In the following, we use the GPU
implementation proposed by \textsc{Dupuy} \textit{et al.}~\cite{dupuy2014quadtrees}. By
using their approach, Morton codes and bitwise operations are optimized to match
with GPU hardware requirements.

@@

Using this spatial datastructure, triangulated mesh can be constructed
from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
triangulation is generated from local triangle patches computed on
local cell configurations. Since triangle patches are locally
computed, such approach is fully parallel and easy to implement on GPU
hardwares. However, since adjacent cells may not have the same depth
on the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
dual meshes
\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.

In the following, we use the extension of MC configurations to handle
adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First this approach constrains the octree
structure in order to make sure that the depth difference between any
two adjacent cells is at most one. Then, \textsc{Lengyel} \emph{et al.} propose
specific MC configurations for such transition cells,  leading to a
crack-free triangulation.

Similarly to original MC algorithm, this approach is perfectly adapted
to GPU hardwares: Given a set of cells (a vector of morton codes),
each triangle patch can be constructed in parallel (done by
in the \emph{geometry shader} in the GPU graphic pipeline).

>>>>

Representing a hierachical structure on GPU is usually challenging since the GPU
memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
to huge payload from cache misses.  Efficient spatial tree encoding can be
achieved using pointerless structures. We use linear quadtrees or octrees to
represent classical quadtree/octree trees, see for instance
\textsc{Gargantini}~\cite{gargantini1982effective}. This structure consists in
indexing each cell by a \emph{Morton code}: the code of children cells are
defined by the code of the parent suffixed by two bits (in dimension 2, three
bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
A cell's code encodes its position \wrt its parent cell and its
complete path to the tree root. Hence, whatever their depth, all cell codes are
simply stored in a linear vector on memory. Furthermore, cell operations such as
subdivision, merging, neighbors access can be efficiently implemented using
bitwise operations on the Morton code. In the following, we use the GPU
implementation proposed by \textsc{Dupuy} \textit{et al.}~\cite{dupuy2014quadtrees}. By
using their approach, Morton codes and bitwise operations are optimized to match
with GPU hardware requirements.

@@

Using this spatial data structure, triangulated mesh can be constructed
from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
triangulation is generated from local triangle patches computed on
local cell configurations. Since triangle patches are locally
computed, such approach is fully parallel and easy to implement on GPU
hardwares. However, since adjacent cells may not have the same depth
on the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
dual meshes
\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.

In the following, we use the extension of MC configurations to handle
adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First, this approach constrains the octree
structure in order to make sure that the depth difference between any
two adjacent cells is at most one. Then, \textsc{Lengyel} \emph{et al.} propose
specific MC configurations for such transition cells,  leading to a
crack-free triangulation.

Similarly to original MC algorithm, this approach is perfectly adapted
to GPU hardwares: Given a set of cells (a vector of morton codes),
each triangle patch can be constructed in parallel (done by
the \emph{geometry shader} in the GPU graphic pipeline).
